---
title: "Basic Webscraping"
output: html_document
---

<style type="text/css">
.table {

    width: 80%;
    margin-left:10%; 
    margin-right:10%;
}
</style>
```{r,setup, echo=FALSE, cache=TRUE}
## numbers >= 10^5 will be denoted in scientific notation,
## and rounded to 2 digits
options(scipen = 3, digits = 3)

rm(list=ls())

library(httr) #get webpage info
library(rvest) #extract parts of the HTML code
library(dplyr)

```

## Exercises

1. Read the HTML content of the following URL with a variable called webpage: https://money.cnn.com/data/us_markets/ At this point, it will also be useful to open this web page in your browser.

```{r}
url = "https://money.cnn.com/data/us_markets/"
webpage = read_html(url)
```

2. Get the session details (status, type, size) of the above mentioned URL.

```{r}
details = html_session(url)
details
```

3. Extract all of the sector names from the “Stock Sectors” table (bottom left of the web page.)

```{r}
tables = webpage %>%
  html_nodes("div table") #extract all tables from website
sectors = html_table(tables)[[2]][,1] #the second table, first column, contains names
sectors
```

4. Extract all of the “3 Month % Change” values from the “Stock Sectors” table.
Stocks Sectors table, so I get other percentage changes from other tables

```{r}
chg3m = html_table(tables)[[2]][,2] #Move to the second column to find the changes
chg3m
```

5. Extract the table “What’s Moving” (top middle of the web page) into a data-frame.

```{r}
whats_moving = html_table(tables)[[1]]
whats_moving
```

6. Re-construct all of the links from the first column of the “What’s Moving” table.
Hint: the base URL is “https://money.cnn.com”

```{r}
base_url = "https://money.cnn.com"
links = webpage %>%
  html_nodes(".wsod_dataTable") %>% #select the specific table, otherwise we'll get other links
  html_nodes(".wsod_symbol") %>%
  html_attr ("href")
whats_moving_links = paste0(base_url,links)
whats_moving_links
```

7. Extract the titles under the “Latest News” section (bottom middle of the web page.)

```{r}
latest_news = webpage %>%
  html_nodes(".HeadlineList li") %>% #find the node using inspect
  html_text #display it as text
latest_news
```

8. To understand the structure of the data in a web page, it is often useful to know what the underlying attributes are of the text you see.
Extract the attributes (and their values) of the HTML element that holds the timestamp underneath the “What’s Moving” table.

9. Extract the values of the blue percentage-bars from the “Trending Tickers” table (bottom right of the web page.)
Hint: in this case, the values are stored under the “class” attribute.

```{r}
trending_tickers = webpage %>% 
  # html_nodes(".cnnBody_Right") %>%
  # html_nodes(".mod-mostpop") %>%
  # html_nodes("tr") %>%
  # html_nodes(".scale") %>% #it's surprising how little reference we need to find the item we're looking for!
  html_nodes(".bars") %>%
  html_attr("class")
trending_tickers
```

10. Get the links of all of the “svg” images on the web page.
