# pre-class

Make sure you commit this often with meaningful messages. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(dplyr))
```

1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```
f1 <- function(string, prefix) { #srting and prefix are the function's arguments
  substr(string, 1, nchar(prefix)) == prefix #take the first characters of string such that it is the same lenght as prefix and test whether it has the same initial characters as prefix
}
#f1 = "test_prefix"

f2 <- function(x) {
  if (length(x) <= 1) return(NULL) #if vector x is less than or equal to 1 element long, do nothing
  x[-length(x)] #drop the last element of the vector
}
#f2 = "drop_element"

f3 <- function(x, y) { #x and y are the function's arguments
  rep(y, length.out = length(x)) #take the values in vector y and replicate them such that it is the same lenght as vector x
}
#f3 = "equal_length"
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?

While `rnorm()` generates a random sample of values of a univariate normal distribution, `MASS::mvrnorm()` produces a sample of a multivariate normal distribution. It seems that `MASS::mvrnorm()` is a more general command since a univariate case can be applied by specifying a variance-covariance matrix (`Sigma`) that takes as value a scalar instead of a matrix.

3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset.

```{r}
lapply(mtcars, function(x) sd(x)/mean(x))
```

4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)

```{r}
lapply(mtcars, typeof) # mtcars is all numeric
sd1=mtcars %>%
  vapply(sd, numeric(1))

df = mtcars #numeric data frame
car_names=rownames(mtcars) #rownames
df[,"car_names"] = car_names #add names as a new column

sd2=df %>%
  vapply(is.numeric, logical(1)) %>%
  df[.] %>% #i don't understand why we need this step!!!
  vapply(sd, numeric(1))

sd1
sd2
all_equal(sd1, sd2) #check if results are the same.
```
